---
title: |
  | Howdy, World!
  | R Markdown Basics
author: | 
  | C. Luke Watson 
  | Michigan State University
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    number_sections: true
---

<!-- This is how you add comments that will not show up in final version -->
<!-- The following will make it so the default for embedded code is to echo -->
<!-- Echo means it prints the code as well as executes the code  -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Why bother learning this?

Short-term: You will use this to turn in your labs and homework.

Long-term: It looks professional. 
However, I admit that I am not sure that this will be the future.
I think this is just as good if not better than MS Word.

# My Cool Section Title

That is a cool section title.
Is there more?

## My Cool Subsection Title

That is a cool subsection title.
Is there more?

### My Cool Subsubsection Title

That is a cool subsubsection title.
Is there more?

#### My Cool Subsubsubsection Title

That is a cool subsubsubsection title.
Is there more?

##### My Cool Subsubsubsection Title

That is a cool subsubsubsubsection title.
Is there more?

No.

# Ok, but what is R Markdown?

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. 
For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

## How to use

First, must use ``install.packages("rmarkdown")`` in \textsf{Rstudio} before use.

## How to Stylize Text

This is a short sentence. It is followed by another without a line break.

This is sentence starts a new paragraph.  
By ending the above text with two ``spaces`` I get a line break but this text is in the same paragraph.

### Fancy text

*italics* and _italics_  
**bold** and __bold__  
superscript^2^  
~~strikethrough~~  

***

> ``Friends show their love in times of trouble, not in happiness.''  
-- Euripides

******

### Lists

Does this work?
* item 1 that I want below
* item 2 that I want below item 1

What about this?

* ah, I need a blank line between 
* my text and my list 
    + for my lists
    + to actually work 

I can also make the lists be ordered:

1. How do I get subitems?
 + one ``space`` -- nope
2. Is this how I get subitems?
  + one ``tab`` -- nope
3. What about this? 
    + two ``tabs`` -- yes!
    
### Tables

Table Header  | Second Header
------------- | ------------- 
Cell 1 | Cell 2
Cell 3 | Cell 4

# The Real Power of Markdown

When you click the **Knit** button a document will be generated that includes both text content as well as: 
<!-- Need a line break to start the list -->

1. the output of any embedded R code chunks within the document
2. any math content you type

## Add R Code 

You can embed an R code chunk like this:

```{r }
set.seed(42)
N <- 1000
x <- rnorm(N, mean=42, sd=10)
mean(x)
summary(x)
```

The default is to have `echo on'.

### Including Plots

You can also embed plots, for example:

```{r , echo=FALSE}
set.seed(42)
N <- 1000
x <- rnorm(N, mean=42, sd=10)
plot(density(x), main="PDF of Random Data and Normal",xlab = NULL)
curve(dnorm(x, mean=42, sd=10), col="darkblue", lwd=2, add=TRUE, yaxt="n")
```

By adding `echo = FALSE` parameter to the code chunk, you prevent the printing of the R code that generated the plot.

### An example with data

<!-- Below I am suppressing errors,warnings, and messages.  -->
<!-- Only do this when you are sure of your code! Heed the code's warnings!  -->

```{r qplot, fig.width=4, fig.height=3,message=FALSE,error=FALSE,warning=FALSE}
# Load libraries
library(tidyverse)
library(fixest)
# Summary, Regression, then Plot
# Cars is a built in dataset
summary(cars)
etable(feols(dist~speed, data=cars))
qplot(speed,dist,data=cars) +
  geom_smooth() +
  geom_smooth(method='lm',color = "red")
```

## Math in Markdown

I like markdown because you can easily type math and it looks very nice.

### Math in Paragraphs

I am writing about the cool equation I learned, 
$y = X \beta + \varepsilon$.
This is a linear equation, but I could also write a non-linear one:
$y = \beta_0 + \beta_1\log(x) + \beta_2 z^2 + \nu$.

### Math in Display Mode
The following equation is important, so I want to number it to remember later:
\begin{equation}
D_j = \frac{\mathsf{e}^{X_{j}\beta}}{1 + \mathsf{e}^{X_{j}\beta}} \label{eq:myeq}.
\end{equation}

Hey, remember equation \ref{eq:myeq}? 
It was cool.

What if I need to show math steps?
Then I would use the `align` environment:
\begin{align}
D_j &= \frac{\mathsf{e}^{X_{j}\beta}}{1 + \mathsf{e}^{X_{j}\beta}} \\
\implies \ln[D_j] &= X_j \beta - \log[1 + \mathsf{e}^{X_j \beta}] \\ 
& \text{and} \nonumber \\
\implies \ln[1 - D_j] &= \underbrace{\ln[1]}_{=0} - \log[1 + \mathsf{e}^{X_j \beta}] \\ 
\implies \log[D_j] - \log[1-D_j] &= X_j \beta,
\end{align}
where the equations are aligned at the equal sign.

Also, look the equation numbers are correctly updating.
